## The R programming language - 

R is a programming language tailor made for data analysis and data visualization. 
The two primary ways to use the R language is as a script, or from a console window. Both are accessible in Rstudio.

To get the most out of the R language, additional packages are needed. R packages contain data, functions, and compiled code that assists with your data analysis or scripting. Packages are stored in a directory called the library.

The install.packages() function will download whatever packages you may need. Useful packages include: 

```{r}
install.packages(tidyverse)
```

## The tidyverse consists of 8 core packages - 

ggplot2 -   data visualization, and applying visual properties to data variables
tidyr   -   data cleaning
readr   -   importing and reading data
dplyr   -   data manipulation
tibble  -   data frame manipulation
purrr   -   functions and vector manipulation
stringr -   string manipulation
forcats -   categorical data storage and factor manipulation

These packages will be expanded on each in their own respective Rmd files. 

## Use the library() function to load a specific package.

```{r}
library(tidyverse)
```


Some R packages contain datasets to use for testing and practicing data analysis tools. 

```{r}
install.packages("palmerpenguins")
library(palmerpenguins)

```



This is an r code block, which can house scripts to run in R studio
```{r title of code block goes here}

```
three tickmarks before and after the code block are the delineators. 